Reaction-diffusion spacial modeling of COVID-19 in Chicago

### 2021-07-19 chicago-spacial-covid.tex
Started parameter table

@@

	We can account for a change in the parameters due to the lockdown by imposing a time dependence on the transmission rates $\beta$:
	\begin{align}
		\beta_{IS} (t) &= \beta_{IS} \left[ \eta_{IS} + (1 - \eta_{IS}) \frac{1 - \tanh[2(t - t_q)]}{2} \right], \\
		\beta_{AS} (t) &= \beta_{AS} \left[ \eta_{AS} + (1 - \eta_{AS}) \frac{1 - \tanh[2(t - t_q)]}{2} \right].
	\end{align}
	This causes the transmission rates $\beta_{IS}$ and $\beta_{AS}$ to decrease abruptly by a factor of $\eta_{IS}$ and $\eta_{AS}$ respectively at the time $t_q$ when the lockdown was imposed.
\end{document}

>>>>

\usepackage{geometry}
\geometry{
	letterpaper,
	total={170mm,257mm},
	left=20mm,
	top=20mm,
}

@@

	We can account for a change in the parameters due to the lockdown by imposing a time dependence on the transmission rates $\beta$:
	\begin{align}
		\beta_{IS} (t) &= \beta_{IS} \left[ \eta_{IS} + (1 - \eta_{IS}) \frac{1 - \tanh[2(t - t_q)]}{2} \right], \\
		\beta_{AS} (t) &= \beta_{AS} \left[ \eta_{AS} + (1 - \eta_{AS}) \frac{1 - \tanh[2(t - t_q)]}{2} \right].
	\end{align}
	This causes the transmission rates $\beta_{IS}$ and $\beta_{AS}$ to decrease abruptly by a factor of $\eta_{IS}$ and $\eta_{AS}$ respectively at the time $t_q$ when the lockdown was imposed.

	\begin{center}
	\begin{tabular}{ c c c c c }
		\hline
		\hline
			&	&	Median ($t_q = 3$)	&	Median ($t_q = 16$)	&	Initial value \\
		\hline
		Population	&	$N$	&	\multicolumn{3}{ c }{2,693,976} \\
		Initial populations & $(I_0, H_0, D_0)$	&	\multicolumn{3}{ c }{$(297, 134, 6)$} \\
		Non COVID-19 death rate [per day]	&	$\mu$	&	\multicolumn{3}{ c }{$5.79 \times 10^{-7}$} \\
		Transmission rate, $S \rightarrow I$ [per day]	&	$\beta_{IS}$	&	$0.35 (0.28-0.41)$	&	$0.32 (0.29-0.35)$	&	$c \in U[0,1]$ \\
		\hline
		\hline
	\end{tabular}
	\end{center}
\end{document}
